### 2020-08-10 data/to-sort.tex
clean up; multi-line strings with indentation

\subsubsection{\!\!\!{\sl Publications}}

\subsubsection*{{\small $(i)$ {\sc Research Papers in Refereed Journals}}}
\medskip

\begin{center}
	\begin{longtable}{|c|c|c|c|}

		\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total}                \\[.4mm]\hline
		\endfirsthead

		\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Year}          & {\bf Thrust Area} & {\bf Other Areas} & {\bf Total} \hspace{1.1cm} \\[.4mm]\hline
		\endhead

		                    &                   &                   &                            \\[-4mm]
		{\em 2018--19}      & 72                & 34                & 106                        \\[.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\em Accepted for}  & 13                & 7                 & 20                         \\
		{\em publication}   &                   &                   &                            \\[0.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\em Submitted} for & 17                & 12                & 29                         \\
		{\em Publication}   &                   &                   &                            \\[0.4mm]\hline
		                    &                   &                   &                            \\[-4mm]
		{\bf Total}         & {\bf 102}         & {\bf 53}          & {\bf 155}                  \\[0.4mm]\hline
	\end{longtable}
\end{center}

\noindent{{\small $(i\text{-}a)$ {\sc Published in the period under review}}}
\medskip

%% YEAR 1 LISTING %%%%%
\noindent{{\small {\bf April 2018--March 2019:}}}
\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}
\begin{enumerate}[leftmargin=27pt]

	\item Aiyappan, S. and Nandakumaran, A.K. and Prakash, Ravi: Generalization of unfolding operator for highly oscillating
	      smooth boundary domains and homogenization, {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art.~86, 30.

	\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
	      four-sphere, {\em Math. Ann.} {\bf 373} (2019), 1329--1339.

	\item\label{ayyer:exclusion-process} Ayyer, A. and Finn, C. and Roy, D.: Matrix product solution of a left-permeable two-species asymmetric exclusion process, {\em Physical Review E} {\bf 97} (2018), 5225.

	\item\label{ayyer:multispecies-juggling} Ayyer, Arvind and Bouttier, J\'{e}r\'{e}mie and Corteel, Sylvie and
	      Linusson, Svante and Nunzi, Fran\c{c}ois: Bumping sequences and multispecies juggling, {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.

	\item   Ayyer, Arvind and Finn, Caley and Roy, Dipankar: The phase diagram for a multispecies left-permeable asymmetric
	      exclusion process, {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.

	\item\label{ayyer:Hilbert-Galton} Ayyer, Arvind and Ramassamy, Sanjay: The {H}ilbert--{G}alton board, {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.

	\item Bagchi, Sayan and  Thangavelu, Sundaram: Weighted norm inequalities for {W}eyl multipliers and Fourier multipliers on the {H}eisenberg group, {\em J. Anal. Math.} {\bf 136} (2018), 1--29.

	\item Baklouti, Ali and Thangavelu, Sundaram: Hardy and {M}iyachi theorems for {H}eisenberg motion groups, {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.

	\item Balhara, Rakesh: Hardy's inequality for the fractional powers of the {G}rushin
	      operator, {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art.~33, 25.

	\item\label{ghosh:political-business-cycle} Basak, G. K. and Ghosh, M. K. and Mukherjee, D.: A stochastic model with inflation,
	      growth and technology for the political business cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.

	\item Basu, Arnab and Ghosh, Mrinal K.: Nonzero-sum risk-sensitive stochastic games on a countable
	      state space, {\em Math. Oper. Res.} {\bf 43} (2018), 516--532.

	\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva
	      and Putinar, Mihai: Simultaneous kernels of matrix {H}adamard powers, {\em Linear Algebra Appl.} {\bf 576} (2019), 142--157.

	\item Bera, Sayani and Verma, Kaushal: Some aspects of shift-like automorphisms of {$\mathbb C^k$},
	      {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 128} (2018), Art.~10, 48.

	\item Bhattacharyya, Tirthankar and Sau, Haripada: Holomorphic functions on the symmetrized
	      bidisk\,---\,realization, interpolation and extension, {\em J. Funct. Anal.} {\bf 274} (2018), 504--524.

	\item Bhimani, Divyang G. and Balhara, Rakesh and Thangavelu,
	      Sundaram: Hermite multipliers on modulation spaces, {\em Analysis and partial differential equations:
			      perspectives from developing countries} {\bf 275} (2019), 42--64.

	\item Biswas, Indranil and D'Mello, Shane and Mukherjee, Ritwik and Pingali, Vamsi P.: Rational cuspidal
	      curves on del-{P}ezzo surfaces, {\em J. Singul.} {\bf 17} (2018), 91--107.

	\item Biswas, Indranil and Pingali, Vamsi Pritham: A characterization of finite vector bundles on
		      {G}auduchon astheno-{K}\"{a}hler manifolds, {\em \'{E}pijournal Geom. Alg\'{e}brique} {\bf 2} (2018), Art.~6, 13.

	\item Biswas, Rahul and Dond, Asha K. and Gudi, Thirupathi: Edge patch-wise local projection stabilized nonconforming
		      {FEM} for the {O}seen problem, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 189--214.

	\item\label{Misra:symm-polydisc} Biswas, Shibananda and Ghosh, Gargi and Misra, Gadadhar and
	      Shyam Roy, Subrata: On reducing submodules
	      of {H}ilbert modules with {${S}_n$}-invariant kernels, {\em J. Funct. Anal.} {\bf 276} (2019), 751--784.

	\item Borah, Diganta and Haridas, Pranav and Verma, Kaushal: Comments on the {G}reen's function of a
	      planar domain, {\em Anal. Math. Phys.} {\bf 8} (2018), 383--414.

	\item Brenner, Susanne C. and Gudi, Thirupathi and Porwal, Kamana
	      and Sung, Li-Yeng: A {M}orley finite element method for an elliptic distributed
	      optimal control problem with pointwise state and control
	      constraints, {\em ESAIM Control Optim. Calc. Var.} {\bf 24} (2018), 1181--1206.

	\item Carstensen, Carsten and Dond, Asha K. and Rabus, Hella: Quasi-optimality of adaptive mixed {FEM}s for non-selfadjoint
	      indefinite second-order linear elliptic problems, {\em Comput. Methods Appl. Math.} {\bf 19} (2019), 233--250.

	\item Chandel, Vikramjeet Singh: The three-point {P}ick--{N}evanlinna interpolation problem on
	      the polydisc, {\em Complex Var. Elliptic Equ.} {\bf 63} (2018), 1341--1352.

	\item\label{rangarajan:Granger-causality} Chopra, R. and Murthy, C. R. and Rangarajan, G.: Statistical tests for detecting Granger causality, {\em IEEE Transactions on Signal Processing} {\bf } (2018), 5803--5816.

	\item Ciaurri, \'{O}scar and Roncal, Luz and Thangavelu, Sundaram: Hardy-type inequalities for fractional powers
	      of the {D}unkl-{H}ermite operator, {\em Proc. Edinb. Math. Soc. (2)} {\bf 61} (2018), 513--544.

	\item Dond, Asha K. and Gudi, Thirupathi: Patch-wise local projection stabilized finite element methods
	      for convection-diffusion-reaction problems, {\em Numer. Methods Partial Differential Equations}
		      {\bf 35} (2019), 638--663.

	\item Dond, Asha K. and Gudi, Thirupathi and Sau, Ramesh Ch.: An error analysis of discontinuous finite element
	      methods for the optimal control problems governed by {S}tokes equation, {\em Numer. Funct. Anal. Optim.}
		      {\bf 40} (2019), 421--460.

	\item Gaddam, Sharat and Gudi, Thirupathi: Inhomogeneous {D}irichlet boundary condition in the {\it a
			      posteriori} error control of the obstacle problem, {\em Comput. Math. Appl.} {\bf 75} (2018), 2311--2327.

	\item Gaddam, Sharat and Gudi, Thirupathi: Bubbles enriched quadratic finite element method for the
	      3{D}-elliptic obstacle problem, {\em Comput. Methods Appl. Math.} {\bf 18} (2018), 223--236.

	\item Gaussier, Herv\'{e} and Seshadri, Harish: Holomorphic motions and complex geometry,
	      {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 301--313.

	\item Gaussier, Herv\'{e} and Seshadri, Harish, On the {G}romov hyperbolicity of convex domains in {$\mathbb
				      C^n$}, {\em Comput. Methods Funct. Theory} {\bf 18} (2018), 617--641.

	\item Ghara, Soumitra and Kumar, Surjit: On the sum of two subnormal kernels, {\em J. Math. Anal. Appl.}
		      {\bf 469} (2019), 1015--1027.

	\item Ghara, Soumitra: The orbit of a bounded operator under the M{\"o}bius group modulo similarity equivalence.

	\item Ghosh, Mrinal K. and Pradhan, Somnath: Risk-sensitive stochastic differential games with reflecting
	      diffusions, {\em Stoch. Anal. Appl.} {\bf 36} (2018), 1--27.

	\item Gudi, Thirupathi and Majumder, Papri: Convergence analysis of finite element method for a parabolic
	      obstacle problem, {\em J. Comput. Appl. Math.} {\bf 357} (2019), 85--102.

	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: Von {N}eumann's inequality for commuting
	      operator-valued multishifts, {\em Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.

	\item Gupta, Rajeev and Ramiz Reza, Md.: Operator space structures on {$\ell^1(n)$}, {\em Houston J. Math.}
		      {\bf 44} (2018), 1205--1212.

	\item Hazra, Somnath: Homogeneous 2-shifts, {\em Complex Anal. Oper. Theory} {\bf 13} (2019), 1729--1763.

	\item\label{iyer:connection-model} Iyer, Srikanth K.: The random connection model: connectivity, edge lengths,
	      and degree distributions, {\em Random Structures Algorithms} {\bf 52} (2018), 283--300.

	\item Kashyap, G. and Bapat, D. and Das, D. and Gowaikar, R.D. and  Amritkar, R.E. and Rangarajan, G. and V. Ravindranath and G. Ambika: Synapse loss and progress of Alzheimer's disease\,--\,A network model,
	      {\em Scientific Reports} {\bf 9} (2019).

	\item Khare, Apoorva and Tao, Terence: Schur polynomials, entrywise positivity preservers, and weak
	      majorization, {\em S\'em. Lothar. Combin.} {\bf 80B,} (2018).

	\item Lin, X. and Kulkarni, P. and Bocci, F. and Schafer, N. and Roy, S. and Tsai, M-Y. and He, Y. and Chen, Y and Rajagopalan, K. and Mooney, S. and Zeng, Y. and Weninger, K. and Grishaev, A. and Onuchic, J. and Levine, H. and Wolynes, P. and Salgia, R. and Rangarajan, G. and Uversky, V. and Orban, J. and Jolly, M. K.: Structural and
	      dynamical order of a disordered protein: molecular insights into conformational
	      switching of PAGE4 at the systems level, {\em Biomolecules} {\bf 9} (2019), 77.

	\item\label{rangarajan:prostate-cancer} Lin, X. and Roy, S. and Jolly, M. K. and Bocci, F. and Schafer, N. P. and Tsai, M.-Y. and Chen, Y. and He, Y. and Grishaev, A. and Weninger, K. and Orban, J. and Kulkarni, P. and Rangarajan, G. and Levine, H. and J. N. Onuchic: PAGE4 and conformational switching: Insights from molecular dynamics simulations and implications for
	      prostate cancer, {\em Journal of Molecular Biology} {\bf 430} (2018), 2422--2438.

	\item Mahajan, Prachi and Verma, Kaushal: A comparison of two biholomorphic invariants, {\em Internat. J. Math.} {\bf 30} (2019), 1950012, 16 pp.

	\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, {\em Banach J. Math. Anal.} {\bf 13} (2019), 174--191.

	\item Manfio, F. and Turgay, N. C. and Upadhyay, A.: Biconservative submanifolds in
		      {$\mathbb{S}^n\times\mathbb{R}$} and
		      {$\mathbb{H}^n\times\mathbb{R}$}, {\em J. Geom. Anal.} {\bf 29} (2019), 283--298.

	\item Manikandan, K. and Vishnu Priya, N. and Senthilvelan, M. and
	      Sankaranarayanan, R.: Deformation of dark solitons in a {$\mathcal{PT}$}-invariant
	      variable coefficients nonlocal nonlinear {S}chr\"{o}dinger
	      equation, {\em Chaos} {\bf 28} (2018), 083103, 12.

	\item Misra, Gadadhar and Pal, Avijit: Curvature inequalities for operators in the {C}owen--{D}ouglas
	      class and localization of the {W}allach set, {\em J. Anal. Math.} {\bf 136} (2018), 31--54.

	\item Misra, Gadadhar and Pal, Avijit and Varughese, Cherian: Contractivity and complete contractivity for finite dimensional Banach spaces, {\em J. Operator Theory} {\bf 82} (2019), 23--47.

	\item Pal, Chandan and Pradhan, Somnath: Risk sensitive control of pure jump processes on a general
	      state space, {\em Stochastics} {\bf 91} (2019), 155--174.

	\item Pal, Ratna and Verma, Kaushal: Ergodic properties of families of {H}\'{e}non maps, {\em Ann. Polon. Math.}
		      {\bf 121} (2018), 45--71.

	\item Paul, Kallol and Sain, Debmalya: Birkhoff--{J}ames orthogonality and its application in the
	      study of geometry of {B}anach space, {\em Advanced topics in mathematical analysis} {\bf } (2019), 245--284.

	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita: Approximate {B}irkhoff--{J}ames orthogonality in the space of
	      bounded linear operators, {\em Linear Algebra Appl.} {\bf 537} (2018), 348--357.

	\item Paul, Kallol and Sain, Debmalya and Mal, Arpita and Mandal,
	      Kalidas: Orthogonality of bounded linear operators on complex {B}anach
	      spaces, {\em Adv. Oper. Theory} {\bf 3} (2018), 699--709.

	\item Pingali, Vamsi P.: A note on the deformed {H}ermitian {Y}ang--{M}ills {PDE}, {\em Complex Var. Elliptic Equ.}
		      {\bf 64} (2019), 503--518.

	\item Pingali, Vamsi Pritham: A note on higher extremal metrics, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 6995--7010.

	\item Pingali, Vamsi Pritham: Representability of {C}hern--{W}eil forms, {\em Math. Z.} {\bf 288} (2018), 629--641.

	\item Pritham Pingali, Vamsi: Existence of coupled {K}\"{a}hler--{E}instein metrics using the
	      continuity method, {\em Internat. J. Math.} {\bf 29} (2018), 1850041, 8.

	\item Reddy, Nanda Kishore: Equality of {L}yapunov and stability exponents for products of
	      isotropic random matrices, {\em Int. Math. Res. Not. IMRN} {\bf } (2019), 606--624.

	\item Reza, Md. Ramiz: Curvature inequalities for operators in the {C}owen--{D}ouglas
	      class of a planar domain, {\em Indiana Univ. Math. J.} {\bf 67} (2018), 1255--1279.

	\item Sain, Debmalya: On extreme contractions and the norm attainment set of a
	      bounded linear operator, {\em Ann. Funct. Anal.} {\bf 10} (2019), 135--143.

	\item Sain, Debmalya: On the norm attainment set of a bounded linear operator, {\em J. Math. Anal. Appl.} {\bf 457} (2018), 67--76.

	\item Sain, Debmalya and Paul, Kallol and Bhunia, Pintu and Bag,
	      Santanu: On the numerical index of polyhedral {B}anach spaces, {\em Linear Algebra Appl.} {\bf 577} (2019), 121--133.

	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: A complete characterization of {B}irkhoff--{J}ames
	      orthogonality in infinite dimensional normed space, {\em J. Operator Theory} {\bf 80} (2018), 399--413.

	\item Sain, Debmalya and Paul, Kallol and Mal, Arpita: On approximate {B}irkhoff--{J}ames orthogonality and normal
	      cones in a normed space, {\em J. Convex Anal.} {\bf 26} (2019), 341--351.

	\item\label{rangarajan:microtremor-method} Sant, D.A. and Parvez, I. A. and Rangarajan, G. and Patel, S. J. and Salam, T. A. S. and Bhatt, M. N.: Subsurface imaging of brown coal bearing Tertiary sedimentaries\,---\,Deccan Trap
	      interface using microtremor method, {\em Journal of Applied Geophysics} {\bf 159} (2018), 362--373.

	\item Seshadri, Harish and Verma, Kaushal: Some aspects of the automorphism groups of domains {\em Handbook of group actions, {V}ol.~{III}} {\bf 40} (2018), 145--174.

	\item Thangavelu, Sundaram: An analogue of {P}fannschmidt's theorem for the {H}eisenberg
	      group, {\em J. Anal.} {\bf 26} (2018), 235--244.

	\item Thangavelu, Sundaram and Naidu Dogga, Venku: {$L^p$}-{$L^2$} estimates for solutions of the wave equation
	      associated to the {G}rushin operator, {\em Adv. Pure Appl. Math.} {\bf 9} (2018), 85--92.

	\item Turgay, Nurettin Cenk and Upadhyay, Abhitosh: On biconservative hypersurfaces in 4-dimensional {R}iemannian
	      space forms, {\em Math. Nachr.} {\bf 292} (2019), 905--921.

	\item Verma, Kaushal: Notes on the boundaries of quadrature domains, {\em Anal. Math. Phys.} {\bf 9} (2019), 617--638.

	\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, Govindan
	      and Lakshmanan, M.: On symmetry preserving and symmetry broken bright, dark and
	      antidark soliton solutions of nonlocal nonlinear {S}chr\"{o}dinger
	      equation, {\em Phys. Lett. A} {\bf 383} (2019), 15--26.
\end{enumerate}

\noindent{{\small {\sl In other areas:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by
	      a certain subset of all {F}ourier coefficients, {\em Publ. Mat.} {\bf 63} (2019), 307--341.

	\item Anamby, Pramath and Das, Soumya: Bounds for the {P}etersson norms of the pullbacks of
		      {S}aito-{K}urokawa lifts, {\em J. Number Theory} {\bf 191} (2018), 289--304.

	\item Arunkumar, G. and Kus, Deniz and Venkatesh, R.: Root multiplicities for {B}orcherds
	      algebras and graph coloring, {\em J. Algebra} {\bf 499} (2018), 538--569.

	\item\label{ayyer:plane-partitions} Ayyer, Arvind and Behrend, Roger E.: Factorization theorems for classical group characters,
	      with applications to alternating sign matrices and plane
	      partitions, {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.

	\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven: Odd partitions in {Y}oung's lattice,
	      {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.

	\item Balodi, Mamta and Palcoux, Sebastien: On {B}oolean intervals of finite groups, {\em J. Combin. Theory Ser. A} {\bf 157}
	      (2018), 49--69.

	\item Benedetti, Carolina and Gonz\'{a}lez D'Le\'{o}n, Rafael S. and Hanusa,
	      Christopher R.H. and Harris, Pamela E. and Khare, Apoorva and
	      Morales, Alejandro H. and Yip, Martha: The volume of the caracol polytope, {\em S\'{e}m. Lothar. Combin.}
	      {\bf 80B} (2018), Art.~87, 12.

	\item Bhosle, Usha N.: Hitchin pairs on reducible curves, {\em Internat. J. Math.} {\bf 29}
	      (2018), 1850015, 49.

	\item B\"{o}cherer, Siegfried and Das, Soumya: Cuspidality and the growth of {F}ourier coefficients of
	      modular forms, {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.

	\item B\"{o}cherer, Siegfried and Das, Soumya: Petersson norms of not necessarily cuspidal {J}acobi
	      modular forms and applications, {\em Adv. Math.} {\bf 336} (2018), 335--376.

	\item Banerjee, Abhishek: On {A}uslander's formula and cohereditary torsion pairs, {\em Commun. Contemp. Math.} {\bf 20} (2018),
	      1750071, 27.

	\item Banerjee, Abhishek: Modular {H}ecke algebras over {M}\"{o}bius categories, {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.

	\item Banerjee, Abhishek: A topological {N}ullstellensatz for tensor-triangulated
	      categories, {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.

	\item Banerjee, Abhishek: Quasimodular {H}ecke algebras and {H}opf actions, {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.

	\item Banerjee, Abhishek: Completions of monoid objects and descent results, {\em J. Algebra} {\bf 507} (2018), 362--399.

	\item Burton, Benjamin A. and Datta, Basudeb and Singh, Nitin and
	      Spreer, Jonathan: A construction principle for tight and minimal triangulations
	      of manifolds, {\em Exp. Math.} {\bf 27} (2018), 22--36.

	\item Choudhury, Projesh Nath and Kannan, M. Rajesh and Sivakumar,
	      K. C.: A note on linear preservers of semipositive and minimally
	      semipositive matrices, {\em Electron. J. Linear Algebra} {\bf 34} (2018), 687--694.

	\item Das, Soumya and Khan, Rizwanur: The third moment of symmetric square {$L$}-functions, {\em Q. J. Math.} {\bf 69} (2018),
	      1063--1087.

	\item Das, Soumya and Kohnen, Winfried: On sign changes of eigenvalues of {S}iegel cusp forms of genus
	      2 in prime powers, {\em Acta Arith.} {\bf 183} (2018), 167--172.

	\item Datta, Basudeb and Maity, Dipendu: Semi-equivelar maps on the torus and the {K}lein bottle are
		      {A}rchimedean, {\em Discrete Math.} {\bf 341} (2018), 3296--3309.

	\item Fritz, Tobias and Gadgil, Siddhartha and Khare, Apoorva and Nielsen, Pace P. and Silberman, Lior and Tao, Terence: Homogeneous length functions on groups, {\em Algebra Number Theory} {\bf 12} (2018), 1773--1786.

	\item\label{gupta:measured-foliations} Gupta, Subhojoy and Wolf, Michael: Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Math Ann.} {\bf 373} (2019), 73--118.

	\item Jha, Abhash Kumar and Sahu, Brundaban: Rankin--{C}ohen brackets on {J}acobi forms of several variables
	      and special values of certain {D}irichlet series, {\em Int. J. Number Theory} {\bf 15} (2019), 925--933.

	\item Khare, Apoorva: Generalized nil-{C}oxeter algebras over discrete complex
	      reflection groups, {\em Trans. Amer. Math. Soc.} {\bf 370} (2018), 2971--2999.

	\item Khare, Apoorva: Generalized nil-Coxeter algebras, {\em S\'em Lothar. Combin.} {\bf 80B,} (2018), No.~29.

	\item Khare, Apoorva and Tikaradze, Akaki: A {C}arlitz--von {S}taudt type theorem for finite rings,
	      {\em Linear Algebra Appl.} {\bf 568} (2019), 106--126.

	\item Krakovski, Roi and Onn, Uri and Singla, Pooja: Regular characters of groups of type {$A_n$} over
	      discrete valuation rings, {\em J. Algebra} {\bf 496} (2018), 116--137.

	\item Maity, Dipendu: Pentagonal maps on the torus and the plane, {\em Beitr. Algebra Geom.} {\bf 60} (2019), 17--37.

	\item Maity, Dipendu and Upadhyay, Ashish Kumar: On centrally symmetric manifolds, {\em J. Ramanujan Math. Soc.} {\bf 34}
	      (2019), 21--27.

	\item Mukherjee, Sajal Kumar and Bera, Sudip: Combinatorial proofs of the {N}ewton--{G}irard and
		      {C}hapman--{C}ostas--{S}antos identities, {\em Discrete Math.} {\bf 342} (2019), 1577--1580.

	\item Narayanan, E. K. and Singla, Pooja: On monomial representations of finitely generated nilpotent
	      groups, {\em Comm. Algebra} {\bf 46} (2018), 2319--2331.

	\item Quddus, Safdar: Invariants of the {$\mathbb Z_2$} orbifolds of the {P}odle\'{s} two
	      spheres, {\em J. Noncommut. Geom.} {\bf 13} (2019), 257--267.

	\item Sanki, Bidyut: Filling of closed surfaces, {\em J. Topol. Anal.} {\bf 10} (2018), 897--913.

	\item Sanki, Bidyut and Gadgil, Siddhartha: Graphs of systoles on hyperbolic surfaces, {\em J. Topol. Anal.}
		      {\bf 11} (2019), 1--20.

\end{enumerate}
\vspace{0.5mm}

%% YEAR 2 LISTING %%%%%
\noindent{{\small {\bf April 2019--March 2020:}}}
\medskip

\noindent{{\small {\sl In the identified thrust area:}}}\vspace{-2.5mm}

\begin{enumerate}[resume, leftmargin=27pt]
	\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
	      Samu: \href{https://doi.org/10.1088/1751-8121/ab2e96}{The exact phase diagram for a
		      semipermeable {TASEP} with nonlocal boundary jumps}, \emph{J. Phys. A} {\bf 52} (2019),
	      355001, 19.

	\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
	      Nandakumaran, A. K.: \href{https://doi.org/10.3233/asy-191526}{Control problem on a rough
		      circular domain and homogenization}, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.

	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1007/s10231-019-00848-7}{Locally periodic unfolding operator for highly oscillating
		      rough domains}, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.

	\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: \href{https://doi.org/10.1142/S0219199719500299}{Semi-linear optimal control problem on a smooth oscillating
		      domain}, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.

	\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: \href{https://doi.org/10.1002/mma.5748}{Asymptotic analysis of a boundary optimal control problem on a general branched structure}, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434.

	\item Aiyappan, S. and Sardar, Bidhan Chandra: \href{https://doi.org/10.1080/00036811.2018.1471207}{Biharmonic equation in a highly oscillating domain and
		      homogenization of an associated control problem}, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.

	\item Anand, Jatin and Bhattacharyya, Tirthankar and Srivastava,
	      Sachi: \href{https://doi.org/10.1007/s00013-019-01406-6}{Some thoughts on composition operators on subspaces of the
			      {H}ardy space}, \emph{Arch. Math. (Basel)} {\bf 114} (2020), 431--444.

	\item Ayyer, Arvind and Behrend, Roger E. and Fischer, Ilse: \href{https://doi.org/10.1016/j.aim.2020.107125}{Extreme diagonally and antidiagonally symmetric alternating
		      sign matrices of odd order}, \emph{Adv. Math.} {\bf 367} (2020), 107125, 56.

	\item Ayyer, Arvind and Behrend, Roger E.: \href{https://doi.org/10.1016/j.jcta.2019.01.001}{Factorization theorems for classical group characters, with
		      applications to alternating sign matrices and plane
		      partitions}, \emph{J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.

	\item Ayyer, Arvind and Fischer, Ilse: \href{https://doi.org/10.1016/j.jcta.2020.105241}{Bijective proofs of skew {S}chur polynomial factorizations}, \emph{J. Combin. Theory Ser. A} {\bf 174} (2020), 105241, 40.

	\item Ayyer, Arvind and Linusson, Svante: \href{https://doi.org/10.1002/rsa.20825}{Reverse juggling processes}, \emph{Random Structures Algorithms} {\bf 55} (2019), 56--72.

	\item\label{ayyer-singla:commutative-rings} Ayyer, Arvind and Singla, Pooja:
	      \href{https://doi.org/10.1007/s10468-019-09864-w}{Random motion on finite rings, {I}: commutative
		      rings}, \emph{Algebr. Represent. Theory} {\bf 23} (2020), 583--604.

	\item Ayyer, Arvind: \href{https://doi.org/10.1007/s00026-019-00480-5}{Squareness for the {M}onopole-{D}imer model}, \emph{Ann. Comb.} {\bf 24} (2020), 237--255.

	\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
	      Verma, Kaushal: \href{https://doi.org/10.1090/proc/14421}{Remarks on the higher dimensional {S}uita conjecture}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 3401--3411.

	\item Bera, Sayani and Pal, Ratna and Verma, Kaushal: \href{https://doi.org/10.1007/s40879-019-00326-7}{A rigidity theorem for {H}\'{e}non maps}, \emph{Eur. J. Math.} {\bf 6} (2020), 508--532.

	\item Bharali, Gautam and Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s11785-017-0701-5}{Pick interpolation on the polydisc: small families of
		      sufficient kernels}, \emph{Complex Anal. Oper. Theory} {\bf 13} (2019), 2069--2093.

	\item Bharali, Gautam: \href{https://doi.org/10.1007/s12220-019-00342-9}{On the growth of the {B}ergman metric near a point of infinite
		      type}, \emph{J. Geom. Anal.} {\bf 30} (2020), 1238--1258.

	\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107.

	\item\label{Bhattacharyya:symm-bidisc} Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz
	      operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} (2020).

	\item Bhattacharyya, Tirthankar and Rao, T. S. S. R. K.: \href{https://doi.org/10.1007/s13226-019-0345-4}{Survey of last ten years of work done in {I}ndia in some
		      selected areas of functional analysis and operator theory}, \emph{Indian J. Pure Appl. Math.} {\bf 50} (2019), 599--617.

	\item Boggarapu, Pradeep and Roncal, Luz and Thangavelu, Sundaram: \href{https://doi.org/10.3934/cpaa.2019116}{On extension problem, trace {H}ardy and {H}ardy's inequalities
		      for some fractional {L}aplacians}, \emph{Commun. Pure Appl. Anal.} {\bf 18} (2019), 2575--2605.

	\item Chakraborty, Atlanta and Chandru, Vijay and Rao, M. R.: \href{https://doi.org/10.1007/s10479-019-03186-2}{A linear programming primer: from {F}ourier to {K}armarkar}, \emph{Ann. Oper. Res.} {\bf 287} (2020), 593--616.

	\item Chandel, Vikramjeet Singh: \href{https://doi.org/10.1007/s12220-018-00123-w}{The 3-point spectral pick interpolation problem and an
		      application to holomorphic correspondences}, \emph{J. Geom. Anal.} {\bf 30} (2020), 551--572.

	\item Cicuttin, Matteo and Ern, Alexandre and Gudi, Thirupathi: \href{https://doi.org/10.1007/s10915-020-01195-z}{Hybrid high-order methods for the elliptic obstacle problem}, \emph{J. Sci. Comput.} {\bf 83} (2020), Paper No. 8, 18.

	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1016/j.camwa.2019.06.022}{Conforming and discontinuous {G}alerkin {FEM} in space for
	      solving parabolic obstacle problem}, \emph{Comput. Math. Appl.} {\bf 78} (2019), 3896--3915.

	\item Gudi, Thirupathi and Majumder, Papri: \href{https://doi.org/10.1515/cmam-2019-0057}{Crouzeix-{R}aviart finite element approximation for the
	      parabolic obstacle problem}, \emph{Comput. Methods Appl. Math.} {\bf 20} (2020), 273--292.

	\item Gupta, Rajeev and Kumar, Surjit and Trivedi, Shailesh: \href{https://doi.org/10.1090/proc/14410}{Von {N}eumann's inequality for commuting operator-valued
		      multishifts}, \emph{Proc. Amer. Math. Soc.} {\bf 147} (2019), 2599--2608.

	\item Iyer, S. K. and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.

	\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).

	\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and  Amritkar, R. E. and Rangarajan, G. and V. Ravindranath and G. Ambika: Synapse loss and progress of Alzheimers disease - A network model, \emph{Scientific Reports} {\bf 9} (2019).

>>>>

\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.

\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
